A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-11-05 CWP/papers/HSF-CWP-2017-01_roadmap/latex/cwp-main.tex
Remove out of place item about people from simulation section
Correct double "the"

\begin{itemize}
\item
  Reviewing the physics models' assumptions, approximations, and
  limitations in order to achieve higher precision, and to extend the
  validity of models up to energies of the order of 100 TeV foreseen
  with the Future Circular Collider (FCC) project~\cite{FCC}.
\item
  Redesigning, developing, and commissioning detector simulation
  toolkits to be more efficient when executed on current vector CPUs and
  emerging new architectures, including GPUs, where use of SIMD
  vectorisation is vital; this includes porting and optimising the
  experiments' simulation applications to allow exploitation of large
  HPC facilities.
\item
  Exploring different Fast Simulation options, where the full detector
  simulation is replaced, in whole or in part, by computationally
  efficient techniques. An area of investigation is common frameworks
  for fast tuning and validation.
\item
  Developing, improving and optimising geometry tools that can be shared
  am\-ong experiments to make the modeling of complex detectors
  computationally more efficient, modular, and transparent.
\item
  Developing techniques for background modeling, including contributions
  of multiple hard interactions overlapping the event of interest in
  collider experiments (pileup).
\item
  Revisiting digitisation algorithms to improve performance and
  exploring opportunities for code sharing among experiments.
\item
  Recruiting, training, retaining human resources in all areas of
  expertise pertaining to the simulation domain, including software and
  physics.
\end{itemize}

@@

The reconstruction of raw detector data and simulated data, and its
processing in real time, represent a major component of today's
computing requirements in HEP. Advances in the capabilities of
facilities and future
experiments bring the potential for a dramatic increase in physics
reach, at the price of increased event complexities and rates. It is
therefore essential that event reconstruction algorithms and software
triggers continue to evolve so that they are able to efficiently exploit
future computing architectures, and deal with the increase in data rates
without loss of physics. Projections into future, e.g., at HL-LHC conditions,
show that without significant changes in approach or algorithms
the increase in resources needed would be incompatible with the
the expected budget.

>>>>

\begin{itemize}
\item
  Reviewing the physics models' assumptions, approximations, and
  limitations in order to achieve higher precision, and to extend the
  validity of models up to energies of the order of 100 TeV foreseen
  with the Future Circular Collider (FCC) project~\cite{FCC}.
\item
  Redesigning, developing, and commissioning detector simulation
  toolkits to be more efficient when executed on current vector CPUs and
  emerging new architectures, including GPUs, where use of SIMD
  vectorisation is vital; this includes porting and optimising the
  experiments' simulation applications to allow exploitation of large
  HPC facilities.
\item
  Exploring different Fast Simulation options, where the full detector
  simulation is replaced, in whole or in part, by computationally
  efficient techniques. An area of investigation is common frameworks
  for fast tuning and validation.
\item
  Developing, improving and optimising geometry tools that can be shared
  am\-ong experiments to make the modeling of complex detectors
  computationally more efficient, modular, and transparent.
\item
  Developing techniques for background modeling, including contributions
  of multiple hard interactions overlapping the event of interest in
  collider experiments (pileup).
\item
  Revisiting digitisation algorithms to improve performance and
  exploring opportunities for code sharing among experiments.
\end{itemize}

@@

The reconstruction of raw detector data and simulated data, and its
processing in real time, represent a major component of today's
computing requirements in HEP. Advances in the capabilities of
facilities and future
experiments bring the potential for a dramatic increase in physics
reach, at the price of increased event complexities and rates. It is
therefore essential that event reconstruction algorithms and software
triggers continue to evolve so that they are able to efficiently exploit
future computing architectures, and deal with the increase in data rates
without loss of physics. Projections into future, e.g., at HL-LHC conditions,
show that without significant changes in approach or algorithms
the increase in resources needed would be incompatible with
the expected budget.
